\newpage
\TOCadd{Acknowledgements}

\begin{center}
ACKNOWLEDGEMENTS
\end{center}

\noindent First, I would like to thank my supervisor \textbf{Dr. George Tzanetakis} for supporting me throughout my whole education at the University of Victoria. His kind, flexible, and positive behaviours during my stressful times were definitely very helpful. He always presented me with his excellent knowledge, ideas, references, and experiences. More specifically, there was a time when I gave up on my idea for this thesis and he encouraged me to continue simply by saying: "I have done enough research to be able to tell if there is hope or not, even if it is not visible in the results yet. We just need to polish it so it shows itself.". So without him, I probably wouldn't have stayed consistent to finally experience success.

Then, I would like to thank \textbf{Dr. Bill Bird} who allowed me to satisfy my dream of understanding and implementing different types of compression schemes in his Data Compression course. It was his excellent and carefully polished course design, videos, presentations, and assignments that made me more interested and able to satisfy my childhood curiosity about this subject.

Being a self-funded student, I would also like to thank \textbf{Leigh Christie}, my work supervisor at MistyWest company who supported me in my half-work half-school life. He cheered me and admired me for staying focused despite being in this splitted lifestyle. I believe studying would have been much more difficult without his acknowledgement, flexibility, and understanding.

Being far away from my home country Iran, I would like to thank my beloved family in Coquitlam, \textbf{Azadeh and Ali Hariri}. They treated me like my genuine mom and dad and they helped me with all different kinds of emotional and financial trauma during the last 5 years of being in Canada. I believe without their help, this thesis would have been delayed even more, I couldn't have the peace of mind, and I couldn't pass through many difficulties that I experienced. I will be in debt for their exceptional support for as long as I live.

Lastly, I would like to thank \textbf{my mom and dad and all my friends} in Iran and in Canada who encouraged me to stay strong, stay consistent, and be hopeful at the times that I felt lonely far away from home and to be mindful of the bright future ahead.

% \noindent I would like to thank:
% \begin{description}
% \item[my cat, Star Trek, and the weather,]
% 	for supporting me in the low moments.
% \item[Supervisor Main,]
% 	for  mentoring, support, encouragement, and patience.
% \item[Grant Organization Name,]
% 	for funding me with a Scholarship.
% \end{description}

% \begin{flushright}
% \textit{I believe I know the only cure, which is to make
% one's centre of life inside of one's self, not
% selfishly or excludingly, but with a kind of
% unassailable serenity-to decorate one's inner house
% so richly that one is content there, glad to welcome
% any one who wants to come and stay, but happy all
% the same in the hours when one is inevitably alone.}
% \\
% Edith Wharton \\
% \end{flushright}
